### 2017-08-17 Tex_Dissertation/MSc_dissertation.tex
morning

In the physical case that I examine what will later be denoted as SUSY signal: corresponding to the 
top squarks, SUSY and SM background: corresponding to any physical process that immitates the one under 
consideration.

To this end, using the TMVA package in root and trainning 1000 trees with the  preselection cuts:

@@

where $E_{visible}$ is the total energy of the jets and $E_{top,i}$ is the energy of the $i^{th}$ top quark.
99$\%$ of the signal events passed the cut whereas for the background 70$\%$.

In what follows I enumerate the input variables in the TMVA that they were used for trainning and testing 
the classifiers. It is important to notice that the sample with which the BDT's was trainned and tested were
different.

>>>>

The products of the particle collision can be separated as signal and background.
The channel of interest is denoted as SUSY signal, i.e.:

The SUSY background is any other SUSY process that involves top squark pair production but the final products 
are not the ones of interest, and the SM background which does not involve any supersymmetric process.

Before the training and testing phase it is possible to impose some constraints to the input kinematic 
variables. They are called preselection cuts.

% In the physical case that I examine what will later be denoted as SUSY signal: corresponding to the 
% top squarks, SUSY and SM background: corresponding to any physical process that immitates the one under 
% consideration.

To this end, using the TMVA package in ROOT and trainning 1000 trees with the  preselection cuts:

@@

where $E_{visible}$ is the total energy of the jets and $E_{top,i}$ is the energy of the $i^{th}$ top quark.
99$\%$ of the signal events pass the preselection cuts whereas for the background 70$\%$.

In what follows I enumerate the input variables in the TMVA that they are used for trainning and testing 
the classifiers. It is important to notice that the sample with which the BDT's was trainned and tested are
different. Some of those variables can be seen in figures 4.3 - 4.6.
